---
title: "Basics"
author: "Benno Pütz"
output: 
  rmarkdown::html_vignette
#  rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{Basics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      collapse = TRUE,
                      comment = "#>"
)
```

```{r setup}
library(clusterLUTs)
```

## Load Atlas File

Atlas file is located in current working directory so simply read it

```{r atlas}
atlas <- read.tree(system.file('extdata/sbm_1_145_0_atlas.mat',
                               package = 'clusterLUTs'))
```

By default a column for individual areas is added if that is not present in the
input file.

## Create LUT files

The LUTs are derived directly from the atlas file with a single call to `treeluts`:

```{r treeluts}
tl <- treeluts(atlas, outdir = '.', basename = 'oct_')
```
This command also creates the `*lut` files in the current directory.

## Visualization

To visualize the LUTs create the tree and plot it

```{r vis}
tr <- tree.ranges(atlas)
tree.ranges.plot(tr, show.tree = TRUE, lwd = 10, lend = 1)
```

Note: The order of colors does NOT correspond to the cluster indices in the atlas file.